My title

### 2024-11-26 paper/paper.qmd
renamed folders

data <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))
print(data)
```

@@

ggplot(data2, aes(x = rating_count, y = rating)) +
  geom_point()

ggplot(data2, aes(x = pages, y = rating)) +
  geom_point()

@@

>>>>

data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
print(data)
```

@@

ggplot(data2, aes(x = rating, y = rating_count)) +
  geom_point() +
  geom_smooth( se =FALSE, color = "red", size = 1)

ggplot(data2, aes(x = rating, y = pages)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = 'red', size = 1)

@@

avg_pages <- aggregate(pages ~ rated_high, data = data, FUN = mean, na.rm = TRUE)

ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Pages by High Rated",
    x = "High Rated (1 = Yes, 0 = No)",
    y = "Average Pages",
    fill = "High Rated"
  ) +
  theme_minimal()

cover_counts <- data %>%
  group_by(rated_high, cover) %>%
  summarise(count = n()) %>%
  ungroup()

ggplot(cover_counts, aes(x = cover, y = count, fill = cover)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ rated_high) +
  labs(title = "Count of Hardcover and Paperback by Rated High",
       x = "Cover Type",
       y = "Count") +
  theme_minimal()
